Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude

### 2016-11-11 RMS/TIE/Final-version/ALL_15-TIE-3480.tex
rename the final-version dir
add months info to bibs

Liu and Layland~\cite{DBLP:journals/jacm/LiuL73} gave a sufficient
condition for the schedulability of a set of $n$ tasks scheduled by
RMS: $\Sigma^n_{i=1}C_i/T_i \le n(2^{1/n}-1)$, where $C_i$ and $T_i$
are the \emph{computation (time) requirement} and the period of task
$\tau_i$, respectively. Two main directions on RMS have been explored
since then. One is to relax the assumptions on the original RMS model,
making it applicable on more systems.  For instance,
\cite{DBLP:conf/rtss/LehoczkySS87,DBLP:journals/rts/SpruntSL89,DBLP:conf/rtss/LehoczkyR92,DBLP:journals/tc/StrosniderLS95}
allow aperiodic tasks in the scheduling,
\cite{DBLP:journals/pe/LeungW82,audsley1993deadline} generalize RMS to
be \emph{deadline-monotonic}, \cite{DBLP:journals/tc/ShaRL90} allows
resource sharing among tasks,
\cite{dhall1978real,DBLP:journals/rts/LopezGDG03,DBLP:journals/tpds/LopezDG04,DBLP:journals/tc/BaruahG03}
extend RMS on multiprocessors, and
\cite{DBLP:journals/rts/OhS94,DBLP:journals/rts/GhoshMMS98,DBLP:journals/tpds/BertossiMR99}
enhance fault-tolerance. The other direction is to generate better
schedulability test conditions for the algorithm and its
extensions~\cite{DBLP:conf/rtss/LehoczkySD89,DBLP:conf/rtss/KuoM91,DBLP:journals/tc/BiniBB03,DBLP:journals/rts/LopezGDG03,DBLP:journals/tc/BaruahG03,gardner1999}. The
RMS algorithm is no doubt of practical importance.

>>>>

Liu and Layland~\cite{DBLP:journals/jacm/LiuL73} gave a sufficient
condition for the schedulability of a set of $n$ tasks scheduled by
RMS: $\Sigma^n_{i=1}C_i/T_i \le n(2^{1/n}-1)$, where $C_i$ and $T_i$
are the \emph{computation (time) requirement} and the period of task
$\tau_i$, respectively. Two main directions on RMS have been explored
since then. One is to relax the assumptions on the original RMS model,
making it applicable on more systems.  For instance,
\cite{DBLP:conf/rtss/LehoczkySS87,DBLP:journals/rts/SpruntSL89,DBLP:conf/rtss/LehoczkyR92,DBLP:journals/tc/StrosniderLS95}
allow aperiodic tasks in the scheduling,
\cite{DBLP:journals/pe/LeungW82,audsley1993deadline} generalize RMS to
be \emph{deadline-monotonic}, \cite{DBLP:journals/tc/ShaRL90} allows
resource sharing among tasks,
\cite{dhall1978real,DBLP:journals/rts/LopezGDG03,DBLP:journals/tpds/LopezDG04,DBLP:journals/tc/BaruahG03}
extend RMS on multiprocessors, and
\cite{DBLP:journals/rts/OhS94,DBLP:journals/rts/GhoshMMS98,DBLP:journals/tpds/BertossiMR99}
enhance fault-tolerance. The other direction is to generate better
schedulability test conditions for the algorithm and its
extensions~\cite{DBLP:conf/rtss/LehoczkySD89,DBLP:conf/rtss/KuoM91,DBLP:journals/tc/BiniBB03,DBLP:journals/rts/LopezGDG03,DBLP:journals/tc/BaruahG03}. The
RMS algorithm is no doubt of practical importance.
